### 2021-09-12 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@7e1fb30781c47bd0a86a8dcf9e9ef05c54084b9a 🚀

%!TEX TS-program = xelatex
\documentclass[10pt,oneside]{article}

@@

\geometry{includemp,
            letterpaper,
            top=1.2in,
            bottom=2.510cm,
            inner=0.5in,
            outer=0.4in,
            marginparwidth=1.95in,
            marginparsep=0.4in}

\usepackage[singlelinecheck=off]{caption}
\captionsetup{
  font={small},
  labelfont={bf},
  format=plain,
  labelsep=quad
}
\usepackage{floatrow}
\floatsetup[figure]{margins=hangright,
              facing=no,
              capposition=beside,
              capbesideposition={center,outside},
              floatwidth=\textwidth}
\floatsetup[table]{margins=hangoutside,
             facing=yes,
             capposition=beside,
             capbesideposition={center,outside},
             floatwidth=\textwidth}

@@

\medskip
\begin{flushleft}
{\small
%
\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
%
\,\textsuperscript{1,2,‡}, %
\href{https://orcid.org/0000-0003-0193-5441}{Salomé\,Bouskila}%
%
\,\textsuperscript{1,‡}, %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{1,3,2}, %
\href{https://orcid.org/0000-0003-4036-977X}{Ceres\,Barros}%
%
\,\textsuperscript{4}, %
\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
%
\,\textsuperscript{5,2}, %
\href{https://orcid.org/0000-0003-0452-6993}{Maxwell J\,Farrell}%
%
\,\textsuperscript{6}, %
\href{https://orcid.org/0000-0002-9935-1366}{Marie-Josée\,Fortin}%
%
\,\textsuperscript{6}, %
\href{https://orcid.org/0000-0003-3220-6161}{Victoria\,Hemming}%
%
\,\textsuperscript{4}, %
\href{https://orcid.org/0000-0002-4104-9463}{Benjamin\,Mercier}%
%
\,\textsuperscript{3,2}, %
\href{https://orcid.org/0000-0002-6004-4027}{Laura J.\,Pollock}%
%
\,\textsuperscript{5}, %
\href{https://orcid.org/0000-0001-5785-8321}{Rogini\,Runghen}%
%
\,\textsuperscript{7}, %
\href{https://orcid.org/0000-0002-3454-0633}{Giulio V.\,Dalla Riva}%
%
\,\textsuperscript{8}, %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2}
\vskip 1em
\textsuperscript{1}\,Département de Sciences Biologiques, Université de
Montréal, Montréal, Canada; \textsuperscript{2}\,Québec Centre for
Biodiversity Sciences, Montréal, Canada; \textsuperscript{3}\,Université
de Sherbrooke, Sherbrooke, Canada; \textsuperscript{4}\,Department of
Forest Resources Management, University of British Columbia, Vancouver,
Canada; \textsuperscript{5}\,Department of Biology, McGill University,
Montréal, Canada; \textsuperscript{6}\,Department of Ecology \&
Evolutionary Biology, University of Toronto, Toronto,
Canada; \textsuperscript{7}\,Centre for Integrative Ecology, School of
Biological Sciences, University of Canterbury, Canterbury, New
Zealand; \textsuperscript{8}\,School of Mathematics and Statistics,
University of Canterbury, Canterbury, New Zealand\\
\textsuperscript{‡}\,These authors contributed equally to the work\\
\vskip 1em
\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
}
\end{flushleft}

@@

\textbf{Abstract}:\,Despite their importance in many ecological
processes, collecting data and information on ecological interactions,
and therefore species interaction networks, is an exceedingly
challenging task. For this reason, large parts of the world have a
deficit of data of which species interact, and what we can expect the
network structure of these interactions to be. As data collection alone
is unlikely to be sufficient at filling these global gaps, community
ecologists must adopt predictive methods. In this contribution we
develop such a method, relying on graph embedding (the extraction of
explanatory latent variables from known graph structures) and transfer
learning (the application of previous solution to novel problems with
limited predictors overlap) in order to assemble a predicted list of
trophic interactions between mammals of Canada. This interaction list is
derived from extensive knowledge of the mammalian food web of Europe,
despite the fact that there are fewer than 5\% of common species between
the two locations. We provide guidance on how this method can be adapted
by substituting some approaches or predictors in order to make it more
generally applicable to a broad family of ecological problems.

@@

In order to transfer the knowledge from the European metaweb to the
Canadian species pool, we performed ancestral character estimation using
a Brownian motion model, which is a conservative approach in the absence
of strong hypotheses about the nature of phylogenetic signal in the
network decomposition (Litsios and Salamin 2012). This uses the
estimated feature vectors for the European mammals to create a state
reconstruction for all species (conceptually something akin to a
trait-based mammalian phylogeny using generality and vulnerability
traits) and allows us to impute the missing (latent) trait data for the
Canadian species that are not already in the European network; as we are
focused on predicting contemporary interactions, we only retained the
values for the tips of the three. We assumed that all traits
(\emph{i.e.} the feature vectors for the left and right subspaces) were
independent, which is a reasonable assumption as every trait/dimension
added to the t-SVD has an \emph{additive} effect to the one before it.
Note that the Upham, Esselstyn, and Jetz (2019) tree itself has some
uncertainty associated to inner nodes of the phylogeny. In this case
study, we have decided to not propagate this uncertainty, as it would
complexify the process. The Brownian motion algorithm returns the
\emph{average} value of the trait, and its upper and lower bounds.
Because we do not estimate other parameters of the traits'
distributions, we considered that every species trait is represented as
a uniform distribution between these bounds; in a situation where the
algorithm would return point values for all simulations, one could in
theory either estimate the parameters of a distribution for each tip, or
draw randomly from the outputs. In all cases, the inferred left and
right sub-spaces for the Canadian species pool (\(\hat{\mathcal{L}}\)
and \(\hat{\mathcal{R}}\)) have entries that are distributions,
representing the range of values for a given species at a given
dimension.

@@

The phylogenetic reconstruction of \(\hat{\mathcal{L}}\) and
\(\hat{\mathcal{R}}\) has an associated uncertainty, represented by the
breadth of the uniform distribution associated to each of their entries.
Therefore, we can use this information to assemble a
\emph{probabilistic} metaweb in the sense of Poisot et al. (2016),
\emph{i.e.} in which every interaction is represented as a single,
independent, Bernoulli event of probability \(p\).

@@

Specifically, we have adopted the following approach. For every entry in
\(\hat{\mathcal{L}}\) and \(\hat{\mathcal{R}}\), we draw a value from
its distribution. This results in one instance of the possible left
(\(\hat{\mathcal{l}}\)) and right (\(\hat{\mathcal{r}}\)) subspaces for
the Canadian metaweb. These can be multiplied, to produce one matrix of
real values. Because the entries in \(\hat{\mathcal{l}}\) and
\(\hat{\mathcal{r}}\) are in the same space where \(\mathcal{L}\) and
\(\mathcal{R}\) were originally predicted, it follows that the threshold
\(\rho\) estimated for the European metaweb also applies. We use this
information to produce one random Canadian metaweb,
\(N = \hat{\mathcal{L}}\)\(\hat{\mathcal{R}}' \ge \rho\). As we can see
in (fig.~\ref{fig:subspaces}) the European and Canadian metawebs are
structurally similar (as would be expected given the biogeographic
similarities) and that the two (left and right) subspaces are distinct
\emph{i.e.} capturing predation (generality) and prey (vulnerability)
traits.

Because the intervals around some trait values can be broad (in fact,
probably broader than what they would actually be, see \emph{e.g.}
Garland, Midford, and Ives 1999), we repeat the above process
\(2\times 10^5\) times, which results in a probabilistic metaweb \(P\),
where the probability of an interaction (here conveying our degree of
trust that it exists given the inferred trait distributions) is given by
the number of times where it appears across all random draws \(N\),
divided by the number of samples. An interaction with \(P_{i,j} = 1\)
means that these two species were predicted to interact in all
\(2\times 10^5\) random draws, etc..

@@

Because the confidence intervals on the inferred trait space are
probably over-estimates, we decided to apply a thresholding step to the
interactions after the data inflation (fig.~\ref{fig:thresholds}).
Cirtwill and Hambäck (2021) proposed a number of strategies to threshold
probabilistic networks. Their methods assume the underlying data to be
tag-based sequencing, which represents interactions as co-occurrences of
predator and prey within the same tags; this is conceptually identical
to our Bernoulli-trial based reconstruction of a probabilistic network.
We performed a full analysis of the effect of various cutoffs, and as
they either resulted in removing too few interactions, or removing
enough interactions that species started to be disconnected from the
network, we set this threshold for a probability equivalent to 0 to the
largest possible value that still allowed all species to have at least
one interaction with a non-zero probability. The need for this slight
deviation from the Cirtwill and Hambäck (2021) method highlights the
need for additional development on network thresholding.

@@

In fig.~\ref{fig:thresholds}, we examine the effect of varying the
cutoff on \(P(i \rightarrow j)\) on the number of links, species, and
connectance. Determining a cutoff using the maximum curvature, or
central difference approximation of the second order partial derivative,
as suggested by \emph{e.g.} Cirtwill and Hambäck (2021), results in
respectively species being lost, or almost all links being kept. We
therefore settled on the value that allowed all species to remain with
at least one interaction. This result, in and of itself, suggests that
additional methodological developments for the thresholding of
probabilistic networks are required.

@@

The t-SVD embedding is able to learn relevant ecological features for
the network. fig.~\ref{fig:degree} shows that the first rank correlates
linearly with generality and vulnerability (Schoener 1989), \emph{i.e.}
the number of preys and predators. Importantly, this implies that a rank
1 approximation represents the configuration model for the metaweb,
\emph{i.e.} a set of random networks generated from a given degree
sequence (Park and Newman 2004). Accounting for the probabilistic nature
of the degrees, the rank 1 approximation also represents the \emph{soft}
configuration model (van der Hoorn, Lippner, and Krioukov 2018). Both
models are maximum entropy graph models (Garlaschelli, Hollander, and
Roccaverde 2018), with sharp (all network realizations satisfy the
specified degree sequence) and soft (network realizations satisfy the
degree sequence on average) local constraints, respectively. The (soft)
configuration model is an unbiased random graph model widely used by
ecologists in the context of null hypothesis significance testing of
network structure (\emph{e.g.} Bascompte et al. 2003) and can provide
informative priors for Bayesian inference of network structure
(\emph{e.g.} J.-G. Young, Cantwell, and Newman 2021). It is noteworthy
that for this metaweb, the relevant information was extracted at the
first rank. Because the first rank corresponds to the leading singular
value of the system, the results of fig.~\ref{fig:degree} have a
straightforward interpretation: degree-based processes are the most
important in structuring the mammalian food web.

@@

One important aspect in which Europe and Canada differ (despite their
comparable bioclimatic conditions) is the legacy of human impacts, which
have been much longer in Europe. Nenzén, Montoya, and Varela (2014)
showed that even at small scales (the Iberian peninsula), mammal food
webs retain the signal of both climate change and human activity, even
when this human activity was orders of magnitude less important than it
is now. Similarly, Yeakel et al. (2014) showed that changes in human
occupation over several centuries can lead to food web collapse.
Megafauna in particular seems to be very sensitive to human arrival
(Pires et al. 2015). In short, there is well-substantiated support for
the idea that human footprint affects more than the risk of species
extinction (Marco et al. 2018), and can lead to changes in interaction
structure. Yet, owing to the inherent plasticity of interactions, there
have been documented instances of food webs undergoing rapid
collapse/recovery cycles over short periods of time (Pedersen et al.
2017). The embedding of a network, in a sense, embeds its
macro-evolutionary history, especially as RDPG captures ecological
signal (Dalla Riva and Stouffer 2016); at this point, it is important to
recall that a metaweb is intended as a catalogue of all possible
interactions, which should then be filtered (Morales-Castilla et al.
2015). In practice (and in this instance) the reconstructed metaweb will
predict interactions that are plausible based on the species'
evolutionary history, however some interactions would not be realized
due to human impact.

Cirtwill et al. (2019) previously made the point that network inference
techniques based on Bayesian approaches would perform far better in the
presence of an interaction-level informative prior; the desirable
properties of such a prior would be that it is expressed as a
probability, preferably representing a Bernoulli event, the value of
which would be representative of relevant biological processes. We argue
that the probability returned at the very last step of our framework may
serve as this informative prior; indeed, the output of our analysis can
be used in subsequent steps, also possibly involving expert elicitation
to validate some of the most strongly recommended interactions. One
important \emph{caveat} to keep in mind when working with interaction
inference is that interactions can never really be true negatives (in
the current state of our methodological framework and data collection
limitations); this renders the task of validating a model through the
usual application of binary classification statistics very difficult
(although see Strydom et al. 2021 for a discussion of alternative
suggestions).

As Herbert (1965) rightfully pointed out, ``{[}y{]}ou can't draw neat
lines around planet-wide problems''; in this regard, our approach must
contend with two interesting problems. The first is the limit of the
metaweb to embed and transfer. If the initial metaweb is too narrow in
scope, notably from a taxonomic point of view, the chances of finding
another area with enough related species to make a reliable inference
decrease. This is notably true if the metaweb is assembled in an area
with mostly endemic species. Conversely, the metaweb should be reliably
filled, which assumes that the \(S^2\) interactions in a pool of \(S\)
species have been examined, either through literature surveys or expert
elicitation. The second problem is to determine which area should be
used to infer the new metaweb in, as this determines the species pool
that must be used. In our application, we focused on the mammals of
Canada. The upside of this approach is that information at the country
level is likely to be required by policy makers and stakeholders for
their biodiversity assessment, as each country tends to set goals at the
national level (Buxton et al. 2021) for which quantitative instruments
are designed (Turak et al. 2017), with specific strategies often enacted
at smaller scales (Ray, Grimm, and Olive 2021). Yet these national
divisions, in large parts of the world, reflect nothing except for the
legacy of settler colonialism, and operating under them must be done
under the clear realization that they contributed to the ongoing
biodiversity crisis (Adam 2014), can reinforce environmental injustice
(Choudry 2013; Domínguez and Luoma 2020), and on Turtle Island
especially, will probably end up being replaced by Indigenous principles
of land management (Eichhorn, Baker, and Griffiths 2019; No'kmaq et al.
2021).

\textbf{Acknowledgements:} We acknowledge that this study was conducted
on land within the traditional unceded territory of the Saint Lawrence
Iroquoian, Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak
nations. TP, TS, DC, and LP received funding from the Canadian Institue
for Ecology \& Evolution. FB is funded by the Institut de Valorisation
des Données. TS, SB, and TP are funded by a donation from the Courtois
Foundation. CB was awarded a Mitacs Elevate Fellowship no. IT12391, in
partnership with fRI Research, and also acknowledges funding from
Alberta Innovates and the Forest Resources Improvement Association of
Alberta. M-JF acknowledges funding from NSERC Discovery Grant and NSERC
CRC RR is funded by New Zealand's Biological Heritage Ngā Koiora Tuku
Iho National Science Challenge, administered by New Zealand Ministry of
Business, Innovation, and Employment. BM is funded by the NSERC
Alexander Graham Bell Canada Graduate Scholarship and the FRQNT master's
scholarshipTP acknowledges financial support from NSERC through the
Discovery Grants and Discovery Accelerator Supplement programs.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Adam2014EleTre}{}%
Adam, Rachelle. 2014. \emph{Elephant Treaties: The Colonial Legacy of
the Biodiversity Crisis}. UPNE.

\leavevmode\hypertarget{ref-Albouy2019MarFis}{}%
Albouy, Camille, Philippe Archambault, Ward Appeltans, Miguel B. Araújo,
David Beauchesne, Kevin Cazelles, Alyssa R. Cirtwill, et al. 2019.
{``The Marine Fish Food Web Is Globally Connected.''} \emph{Nature
Ecology \& Evolution} 3 (8): 1153--61.
\url{https://doi.org/10.1038/s41559-019-0950-y}.

\leavevmode\hypertarget{ref-Banville2021ManJl}{}%
Banville, Francis, Steve Vissault, and Timothée Poisot. 2021.
{``Mangal.jl and EcologicalNetworks.jl: Two Complementary Packages for
Analyzing Ecological Networks in Julia.''} \emph{Journal of Open Source
Software} 6 (61): 2721. \url{https://doi.org/10.21105/joss.02721}.

\leavevmode\hypertarget{ref-Bascompte2003NesAss}{}%
Bascompte, J., P. Jordano, C. J. Melian, and J. M. Olesen. 2003. {``The
Nested Assembly of Plant-Animal Mutualistic Networks.''}
\emph{Proceedings of the National Academy of Sciences} 100 (16):
9383--87. \url{https://doi.org/10.1073/pnas.1633576100}.

\leavevmode\hypertarget{ref-Beckerman2006ForBio}{}%
Beckerman, Andrew P., Owen L. Petchey, and Philip H. Warren. 2006.
{``Foraging Biology Predicts Food Web Complexity.''} \emph{Proceedings
of the National Academy of Sciences} 103 (37): 13745--49.
\url{https://doi.org/10.1073/pnas.0603039103}.

>>>>

%!TEX TS-program = xelatex
\documentclass[10pt,oneside]{article}
\usepackage[fontsize=9pt]{scrextend}

@@

\geometry{includemp,
            letterpaper,
            top=1.0in,
            bottom=2.510cm,
            left=0.35in,
            right=0.35in,
            marginparwidth=2.0in,
            marginparsep=0.35in}

\usepackage[singlelinecheck=off]{caption}
\captionsetup{
  font={small},
  labelfont={bf},
  format=plain,
  labelsep=quad
}

\usepackage{floatrow}

\floatsetup[figure]{margins=hangright,
              facing=no,
              capposition=beside,
              capbesideposition={center,outside},
              floatwidth=\textwidth}

% \floatsetup[table]{margins=hangright,
%              facing=no,
%              capposition=beside,
%              capbesideposition={center,outside},
%              floatwidth=\textwidth}

@@

\medskip
\begin{flushleft}
{\small
%
\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
%
\,\textsuperscript{1,2,‡}, %
\href{https://orcid.org/0000-0003-0193-5441}{Salomé\,Bouskila}%
%
\,\textsuperscript{1,‡}, %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{1,3,2}, %
\href{https://orcid.org/0000-0003-4036-977X}{Ceres\,Barros}%
%
\,\textsuperscript{4}, %
\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
%
\,\textsuperscript{5,2}, %
\href{https://orcid.org/0000-0003-0452-6993}{Maxwell J\,Farrell}%
%
\,\textsuperscript{6}, %
\href{https://orcid.org/0000-0002-9935-1366}{Marie-Josée\,Fortin}%
%
\,\textsuperscript{6}, %
\href{https://orcid.org/0000-0003-3220-6161}{Victoria\,Hemming}%
%
\,\textsuperscript{4}, %
\href{https://orcid.org/0000-0002-4104-9463}{Benjamin\,Mercier}%
%
\,\textsuperscript{3,2}, %
\href{https://orcid.org/0000-0002-6004-4027}{Laura J.\,Pollock}%
%
\,\textsuperscript{5,2}, %
\href{https://orcid.org/0000-0001-5785-8321}{Rogini\,Runghen}%
%
\,\textsuperscript{7}, %
\href{https://orcid.org/0000-0002-3454-0633}{Giulio V.\,Dalla Riva}%
%
\,\textsuperscript{8}, %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2}
\vskip 1em
\textsuperscript{1}\,Département de Sciences Biologiques, Université de
Montréal, Montréal, Canada; \textsuperscript{2}\,Québec Centre for
Biodiversity Sciences, Montréal, Canada; \textsuperscript{3}\,Université
de Sherbrooke, Sherbrooke, Canada; \textsuperscript{4}\,Department of
Forest Resources Management, University of British Columbia, Vancouver,
Canada; \textsuperscript{5}\,Department of Biology, McGill University,
Montréal, Canada; \textsuperscript{6}\,Department of Ecology \&
Evolutionary Biology, University of Toronto, Toronto,
Canada; \textsuperscript{7}\,Centre for Integrative Ecology, School of
Biological Sciences, University of Canterbury, Canterbury, New
Zealand; \textsuperscript{8}\,School of Mathematics and Statistics,
University of Canterbury, Canterbury, New Zealand\\
\textsuperscript{‡}\,These authors contributed equally to the work\\
\vskip 1em
\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
}
\end{flushleft}

@@

Despite their importance in many ecological processes, collecting data
and information on ecological interactions, and therefore species
interaction networks, is an exceedingly challenging task. For this
reason, large parts of the world have a data deficit when it comes to
species interactions, and how the resulting networks are structured. As
data collection alone is unlikely to be sufficient at filling these
global gaps, community ecologists must adopt predictive methods. In this
contribution, we develop such a method, relying on graph embedding (the
extraction of explanatory latent variables from known graph structures)
and transfer learning (the application of previous solutions to novel
problems with limited predictors overlap) in order to assemble a
predicted list of trophic interactions between mammals of Canada. This
interaction list is derived from extensive knowledge of the mammalian
food web of Europe, despite the fact that there are fewer than 5\% of
common species between the two locations. The results of the predictive
model are compared against databases of recorded pairwise interactions,
showing that we correctly recover over 95\% of known interactions. We
provide guidance on how this method can be adapted by substituting some
approaches or predictors in order to make it more generally applicable.

@@

In order to transfer the knowledge from the European metaweb to the
Canadian species pool, we performed ancestral character estimation using
a Brownian motion model, which is a conservative approach in the absence
of strong hypotheses about the nature of phylogenetic signal in the
network decomposition (Litsios \& Salamin 2012). This uses the estimated
feature vectors for the European mammals to create a state
reconstruction for all species (conceptually something akin to a
trait-based mammalian phylogeny using generality and vulnerability
traits) and allows us to impute the missing (latent) trait data for the
Canadian species that are not already in the European network; as we are
focused on predicting contemporary interactions, we only retained the
values for the tips of the tree. We assumed that all traits (\emph{i.e.}
the feature vectors for the left and right subspaces) were independent,
which is a reasonable assumption as every trait/dimension added to the
t-SVD has an \emph{additive} effect to the one before it. Note that the
Upham \emph{et al.} (2019) tree itself has some uncertainty associated
to inner nodes of the phylogeny. In this case study, we have decided to
not propagate this uncertainty, as it would complexify the process. The
Brownian motion algorithm returns the \emph{average} value of the trait,
and its upper and lower bounds. Because we do not estimate other
parameters of the traits' distributions, we considered that every
species trait is represented as a uniform distribution between these
bounds; in a situation where the algorithm would return point values for
all simulations, one could in theory either estimate the parameters of a
distribution for each tip, or draw randomly from the outputs. In all
cases, the inferred left and right sub-spaces for the Canadian species
pool (\(\hat{\mathcal{L}}\) and \(\hat{\mathcal{R}}\)) have entries that
are distributions, representing the range of values for a given species
at a given dimension.

@@

The phylogenetic reconstruction of \(\hat{\mathcal{L}}\) and
\(\hat{\mathcal{R}}\) has an associated uncertainty, represented by the
breadth of the uniform distribution associated to each of their entries.
Therefore, we can use this information to assemble a
\emph{probabilistic} metaweb in the sense of Poisot \emph{et al.}
(2016), \emph{i.e.} in which every interaction is represented as a
single, independent, Bernoulli event of probability \(p\).

@@

Specifically, we have adopted the following approach. For every entry in
\(\hat{\mathcal{L}}\) and \(\hat{\mathcal{R}}\), we draw a value from
its distribution. This results in one instance of the possible left
(\(\hat{\mathcal{l}}\)) and right (\(\hat{\mathcal{r}}\)) subspaces for
the Canadian metaweb. These can be multiplied, to produce one matrix of
real values. Because the entries in \(\hat{\mathcal{l}}\) and
\(\hat{\mathcal{r}}\) are in the same space where \(\mathcal{L}\) and
\(\mathcal{R}\) were originally predicted, it follows that the threshold
\(\rho\) estimated for the European metaweb also applies. We use this
information to produce one random Canadian metaweb,
\(N = \hat{\mathcal{L}}\)\(\hat{\mathcal{R}}' \ge \rho\). As we can see
in (fig.~\ref{fig:subspaces}) the European and Canadian metawebs are
structurally similar (as would be expected given the biogeographic
similarities) and the two (left and right) subspaces are distinct
\emph{i.e.} capturing predation (generality) and prey (vulnerability)
traits.

Because the intervals around some trait values can be broad (in fact,
probably broader than what they would actually be, see \emph{e.g.}
Garland \emph{et al.} 1999), we repeat the above process
\(2\times 10^5\) times, which results in a probabilistic metaweb \(P\),
where the probability of an interaction (here conveying our degree of
trust that it exists given the inferred trait distributions) is given by
the number of times where it appears across all random draws \(N\),
divided by the number of samples. An interaction with \(P_{i,j} = 1\)
means that these two species were predicted to interact in all
\(2\times 10^5\) random draws.

@@

Because the confidence intervals on the inferred trait space are
probably over-estimates, we decided to apply a thresholding step to the
interactions after the data inflation (fig.~\ref{fig:thresholds}).
Cirtwill \& Hambäck (2021) proposed a number of strategies to threshold
probabilistic networks. Their methods assume the underlying data to be
tag-based sequencing, which represents interactions as co-occurrences of
predator and prey within the same tags; this is conceptually identical
to our Bernoulli-trial based reconstruction of a probabilistic network.
We performed a full analysis of the effect of various cutoffs, and as
they either resulted in removing too few interactions, or removing
enough interactions that species started to be disconnected from the
network, we set this threshold for a probability equivalent to 0 to the
largest possible value that still allowed all species to have at least
one interaction with a non-zero probability. The need for this slight
deviation from the Cirtwill \& Hambäck (2021) method highlights the need
for additional development on network thresholding.

@@

In fig.~\ref{fig:thresholds}, we examine the effect of varying the
cutoff on \(P(i \rightarrow j)\) on the number of links, species, and
connectance. Determining a cutoff using the maximum curvature, or
central difference approximation of the second order partial derivative,
as suggested by \emph{e.g.} Cirtwill \& Hambäck (2021), results in
species being lost, or almost all links being kept. We therefore settled
on the value that allowed all species to remain with at least one
interaction. This result, in and of itself, suggests that additional
methodological developments for the thresholding of probabilistic
networks are required.

@@

The t-SVD embedding is able to learn relevant ecological features for
the network. fig.~\ref{fig:degree} shows that the first rank correlates
linearly with generality and vulnerability (Schoener 1989), \emph{i.e.}
the number of preys and predators. Importantly, this implies that a rank
1 approximation represents the configuration model for the metaweb,
\emph{i.e.} a set of random networks generated from a given degree
sequence (Park \& Newman 2004). Accounting for the probabilistic nature
of the degrees, the rank 1 approximation also represents the \emph{soft}
configuration model (van der Hoorn \emph{et al.} 2018). Both models are
maximum entropy graph models (Garlaschelli \emph{et al.} 2018), with
sharp (all network realizations satisfy the specified degree sequence)
and soft (network realizations satisfy the degree sequence on average)
local constraints, respectively. The (soft) configuration model is an
unbiased random graph model widely used by ecologists in the context of
null hypothesis significance testing of network structure (\emph{e.g.}
Bascompte \emph{et al.} 2003) and can provide informative priors for
Bayesian inference of network structure (\emph{e.g.} Young \emph{et al.}
2021). It is noteworthy that for this metaweb, the relevant information
was extracted at the first rank. Because the first rank corresponds to
the leading singular value of the system, the results of
fig.~\ref{fig:degree} have a straightforward interpretation:
degree-based processes are the most important in structuring the
mammalian food web.

@@

One important aspect in which Europe and Canada differ (despite their
comparable bioclimatic conditions) is the degree of the legacy of human
impacts, which have been much longer in Europe. Nenzén \emph{et al.}
(2014) showed that even at small scales (the Iberian peninsula), mammal
food webs retain the signal of both climate change and human activity,
even when this human activity was orders of magnitude less important
than it is now. Similarly, Yeakel \emph{et al.} (2014) showed that
changes in human occupation over several centuries can lead to food web
collapse. Megafauna in particular seems to be very sensitive to human
arrival (Pires \emph{et al.} 2015). In short, there is
well-substantiated support for the idea that human footprint affects
more than the risk of species extinction (Marco \emph{et al.} 2018), and
can lead to changes in interaction structure. Yet, owing to the inherent
plasticity of interactions, there have been documented instances of food
webs undergoing rapid collapse/recovery cycles over short periods of
time (Pedersen \emph{et al.} 2017). The embedding of a network, in a
sense, embeds its macro-evolutionary history, especially as RDPG
captures ecological signal (Dalla Riva \& Stouffer 2016); at this point,
it is important to recall that a metaweb is intended as a catalogue of
all possible interactions, which should then be filtered
(Morales-Castilla \emph{et al.} 2015). In practice (and in this
instance) the reconstructed metaweb will predict interactions that are
plausible based on the species' evolutionary history, however some
interactions would not be realized due to human impact.

Cirtwill \emph{et al.} (2019) previously made the point that network
inference techniques based on Bayesian approaches would perform far
better in the presence of an interaction-level informative prior; the
desirable properties of such a prior would be that it is expressed as a
probability, preferably representing a Bernoulli event, the value of
which would be representative of relevant biological processes
(probability of predation in this case). We argue that the probability
returned at the very last step of our framework may serve as this
informative prior; indeed, the output of our analysis can be used in
subsequent steps, also possibly involving expert elicitation to validate
some of the most strongly recommended interactions. One important
\emph{caveat} to keep in mind when working with interaction inference is
that interactions can never really be true negatives (in the current
state of our methodological framework and data collection limitations);
this renders the task of validating a model through the usual
application of binary classification statistics very difficult (although
see Strydom \emph{et al.} 2021a for a discussion of alternative
suggestions). The other way through which our framework can be improved
is by substituting the predictors that are used for transfer. For
example, in the presence of information on species traits that are known
to be predictive of species interactions, one might want to rely on
functional rather than phylogenetic distances -- in food webs, body size
(and allometrically related variables) has been established as such a
variable (Brose \emph{et al.} 2006); the identification of relevant
functional traits is facilitated by recent methodological developments
(Rosado \emph{et al.} 2013). It should be noted that Xing \& Fayle
(2021) highlight phylogenetic relatedness as one of the core components
of network comparison at the global scale. In this case study, we have
embedded the original metaweb using t-SVD, because it lends itself to a
RDPG reconstruction, which is known to capture the consequences of
evolutionary processes (Dalla Riva \& Stouffer 2016); this being said,
there are others ways to embed graphs (Cai \emph{et al.} 2017; Arsov \&
Mirceva 2019; Cao \emph{et al.} 2019), which can be used as
alternatives.

As Herbert (1965) rightfully pointed out, ``{[}y{]}ou can't draw neat
lines around planet-wide problems''; in this regard, our approach must
contend with two interesting problems. The first is the limit of the
metaweb to embed and transfer. If the initial metaweb is too narrow in
scope, notably from a taxonomic point of view, the chances of finding
another area with enough related species to make a reliable inference
decrease. This is notably true if the metaweb is assembled in an area
with mostly endemic species. Conversely, the metaweb should be reliably
filled, which assumes that the \(S^2\) interactions in a pool of \(S\)
species have been examined, either through literature surveys or expert
elicitation. The second problem is to determine which area should be
used to infer the new metaweb in, as this determines the species pool
that must be used. In our application, we focused on the mammals of
Canada. The upside of this approach is that information at the country
level is likely to be required by policy makers and stakeholders for
their biodiversity assessment, as each country tends to set goals at the
national level (Buxton \emph{et al.} 2021) for which quantitative
instruments are designed (Turak \emph{et al.} 2017), with specific
strategies often enacted at smaller scales (Ray \emph{et al.} 2021). Yet
these national divisions, in large parts of the world, reflect nothing
except for the legacy of settler colonialism, and operating under them
must be done under the clear realization that they contributed to the
ongoing biodiversity crisis (Adam 2014), can reinforce environmental
injustice (Choudry 2013; Domínguez \& Luoma 2020), and on Turtle Island
especially, will probably end up being replaced by Indigenous principles
of land management (Eichhorn \emph{et al.} 2019; No'kmaq \emph{et al.}
2021).

\textbf{Acknowledgements:} We acknowledge that this study was conducted
on land within the traditional unceded territory of the Saint Lawrence
Iroquoian, Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak
nations. TP, TS, DC, and LP received funding from the Canadian Institue
for Ecology \& Evolution. FB is funded by the Institut de Valorisation
des Données. TS, SB, and TP are funded by a donation from the Courtois
Foundation. CB was awarded a Mitacs Elevate Fellowship no. IT12391, in
partnership with fRI Research, and also acknowledges funding from
Alberta Innovates and the Forest Resources Improvement Association of
Alberta. M-JF acknowledges funding from NSERC Discovery Grant and NSERC
CRC. RR is funded by New Zealand's Biological Heritage Ngā Koiora Tuku
Iho National Science Challenge, administered by New Zealand Ministry of
Business, Innovation, and Employment. BM is funded by the NSERC
Alexander Graham Bell Canada Graduate Scholarship and the FRQNT master's
scholarship. LP acknowledges funding from NSERC Discovery Grant (NSERC
RGPIN-2019-05771). TP acknowledges financial support from NSERC through
the Discovery Grants and Discovery Accelerator Supplement programs.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Adam2014EleTre}{}%
Adam, R. (2014). \emph{Elephant treaties: The Colonial legacy of the
biodiversity crisis}. UPNE.

\leavevmode\hypertarget{ref-Albouy2019MarFis}{}%
Albouy, C., Archambault, P., Appeltans, W., Araújo, M.B., Beauchesne,
D., Cazelles, K., \emph{et al.} (2019). The marine fish food web is
globally connected. \emph{Nature Ecology \& Evolution}, 3, 1153--1161.

\leavevmode\hypertarget{ref-Arsov2019NetEmb}{}%
Arsov, N. \& Mirceva, G. (2019). Network Embedding: An Overview.
\emph{arXiv:1911.11726 {[}cs, stat{]}}.

\leavevmode\hypertarget{ref-Banville2021ManJl}{}%
Banville, F., Vissault, S. \& Poisot, T. (2021). Mangal.jl and
EcologicalNetworks.jl: Two complementary packages for analyzing
ecological networks in Julia. \emph{Journal of Open Source Software}, 6,
2721.

\leavevmode\hypertarget{ref-Bascompte2003NesAss}{}%
Bascompte, J., Jordano, P., Melian, C.J. \& Olesen, J.M. (2003). The
nested assembly of plant-animal mutualistic networks. \emph{Proceedings
of the National Academy of Sciences}, 100, 9383--9387.

\leavevmode\hypertarget{ref-Beckerman2006ForBio}{}%
Beckerman, A.P., Petchey, O.L. \& Warren, P.H. (2006). Foraging biology
predicts food web complexity. \emph{Proceedings of the National Academy
of Sciences}, 103, 13745--13749.
